\documentclass[margin]{res}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}
	% Center the name over the entire width of resume:
	\moveleft.5\hoffset\centerline{\large\bf Jo\~{a}o RODRIGUES AM\'{E}RICO}
	% Draw a horizontal line the whole width of resume:
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
	\moveleft.5\hoffset\centerline{jc$@$jcamerico.com $|$ http://www.jcamerico.com $|$ https://github.com/jcamerico}
	\vspace{-5mm}
	\begin{resume}
		\section{OBJECTIVE}  A position of Lead developer, Tech lead or Architect.
		\vspace{-2mm}
		\section{EXPERIENCE} 
			\textbf{Tech Lead} at {\sl TotalEnergies Digital Factory}, Paris, France \hfill Apr 2022 - present\\
                 	\begin{small}              
	                 	{\color{darkgray} Leading squads to build MVPs to digitalize TotalEnergies processes.}\\
		                 {\color{gray}Azure, Java 17, SpringBoot, Angular, Github Actions, Gradle, Gherkin, Playwright, Terraform.}
        	         	\end{small}
			\textbf{Senior Software Engineer} at {\sl Murex S.A.S.}, Paris, France \hfill Nov 2013 - Mar 2022\\
                 	\begin{small}              
	                 	{\color{darkgray} Lead and managed a distributed team working on MX.3's workflow engine.}\\
		                 {\color{gray}Java 6-11, Maven, Camel, ActiveMQ, Spring, Jenkins, Cucumber, Git, SAFe.}
        	         	\end{small}
	              	\vspace{1mm}\\
			\textbf{R\&D Engineer} at {\sl Bull S.A.S.}, Grenoble, France \hfill Nov 2010 - Oct 2013\\
                 	\begin{small}              
                 		{\color{darkgray} Developed models and extensions for real-time support in SOA technologies.}\\
			         {\color{gray}Java, TuSCAny, OSGi, RTSJ.}
        		         \end{small}
               		\vspace{1mm}\\
	                \textbf{Intern} at {\sl Grenoble Informatics Laboratory}, Grenoble, France \hfill Fev 2010 - Aug 2010 \\
        		         \begin{small}
                 		{\color{darkgray} Developed support for real-time applications on the OSGi platform.}\\
				{\color{gray}Java, Apache Karaf, OSGi, RTSJ.}
	                 \end{small}
			\vspace{1mm}\\                 
                		\textbf{Intern} at {\sl Bull S.A.S.}, Grenoble, France \hfill Mar 2009 - Aug 2009 \\
	                \begin{small}
                			{\color{darkgray} Prototyped a real-time Java application server by means of byte-code injection.}\\
				{\color{gray}Java, OSGi, JOnAS, byte-code.}
        		        \end{small}
                		\vspace{1mm}\\                 
		\vspace{-8mm}
		\section{EDUCATION} {\sl Doctorate (PhD),} Computer Science \hfill Nov 2010 - Nov 2013\\
               		University of Grenoble, Grenoble, France\\
	   		\begin{small}
        	        			{\color{darkgray} Thesis: ``A service-oriented component meta-model for developing flexible and modular real-time applications", supervised by Prof. Dr. Didier Donsez.}
				\vspace{1.5mm}\\                 	            
			\end{small}  	            
        		        {\sl Engineer (MSc),} Computer Science (GPA: 14.7/20) \hfill Sep 2008 - Jul 2010\\
               		Grenoble Institute of Technology (ENSIMAG), Grenoble, France.\\
	               	 \begin{small}
        		       		{\color{darkgray} Concentration: Software Engineering and Information Systems. Obtained \textit{Mention Bien}.}
				\vspace{1.5mm}\\
	               	\end{small}
        		        {\sl Bachelor (BSc),} Computer Science (GPA: 9.55/10) \hfill Mar 2005 - Sep 2010\\
                		Federal University of Rio Grande do Sul (UFRGS), Porto Alegre, Brazil\\
	               	\begin{small}
        		       		{\color{darkgray} Academic distinction (\textit{summa cum laude}) and highlight student awards.}
				\vspace{1.5mm}\\
	               	\end{small}
		\vspace{-8mm}
		\section{COMPETENCES} {\sl Portuguese:} Native \hfill {\sl French:} Fluent (oral/written) \hfill {\sl English:} Fluent (oral/written)\\
			{\sl Programming Languages:} Java (expert), Javascript, Python (beginner)\\
		\vspace{-6mm}
		\section{SELECTED PUBLICATIONS} 	
			$\bullet$ {\bf Am\'{e}rico JC}, Rudametkin W, Donsez D. ``Managing the Dynamism of Real-Time Java Applications on the OSGi Platform". In {\sl 27th ACM Symposium on Applied Computing}, Riva del Garda, Italy, 2012. 
			\vspace{1mm}\\
			$\bullet$ Calmant T, {\bf Am\'{e}rico JC}, Donsez D, Gattaz O, Gama K. ``A Dynamic and Service-Oriented Component Model for Python Long-Lived Applications". In {\sl 15th Intl Symposium on Component Based Software Engineering}, Bertinoro, Italy, 2012.
			\vspace{1mm}\\
			$\bullet$ {\bf Am\'{e}rico JC}, Donsez D. ``Service Component Architecture Extensions for Dynamic Systems". In {\sl 10th Intl Conference on Service-Oriented Computing}, Shanghai, China, 2012.
			\vspace{-2mm} 
		\section{PATENTS} 	
			$\bullet$ {\bf FR3012896} - {\sl A procedure to validate the response time of an application, and a procedure to deploy applications using the validation procedure}, May 2015.
			\vspace{1mm}\\
			$\bullet$ {\bf FR3029658} - {\sl System and method for converting octal Java code into real-time octal Java code}, June 2016.
			\vspace{-2mm} 
		\section{INTERESTS} Java, software engineering, volleyball, games, gadgets
	\end{resume}
\end{document}




